Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-07 csf-2017/paper.tex
public future regions

% The future world relation are really the ones from thm, the above
% are properties of them.
{\bf Future world relations}
There are two future world relations a \emph{public future world}
relation and a \emph{private future world} relation. In both future
world relations, we have extension ordering, so a future world $W'$ of
$W$ has at least the same regions as $W$, but $W'$ may have new regions
imposing new protocols on parts of the memory. The two future world
relations differ in the way existing regions are allowed to evolve. In
a \emph{public future world}, the regions are allowed to evolve
according to the \emph{public future region} relation. In a
\emph{private future world}, the regions are allowed to evolve
according to the \emph{private future world} relation. The future
world relations are defined as follows:
\begin{mathpar}
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurewk W(r) }
  { W' \futurewk W }
  \and
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurestr W(r) }
  { W' \futurestr W }
\end{mathpar}

% Relate to STSs for high-level languages. Have the public-private
% transitions, but they are also used for more than this

>>>>

% The future world relation are really the ones from thm, the above
% are properties of them.
{\bf Future world relations}
There are two future world relations a \emph{public future world}
relation and a \emph{private future world} relation. In both future
world relations, we have extension ordering, so a future world $W'$ of
$W$ has at least the same regions as $W$, but $W'$ may have new regions
imposing new protocols on parts of the memory. The two future world
relations differ in the way existing regions are allowed to
evolve. The public future world relation uses the public future region
relation and the private future world relation uses the private future
region relation:
\begin{mathpar}
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurewk W(r) }
  { W' \futurewk W }
  \and
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurestr W(r) }
  { W' \futurestr W }
\end{mathpar}

% Relate to STSs for high-level languages. Have the public-private
% transitions, but they are also used for more than this
\todo[inline]{Relate to STSs for high-level languages?}
